The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Add discussion of Gomez azimuthal variations

The other set of simulations are isolated N-body simulations of interactions between the Milky Way and a Sagittarius-like dwarf galaxy, described briefly in \S \ref{ssec:sag_sim}. These include dark matter and stars and are tailored to existing measurements of the structure of the Milky Way's disk and of the orbit and properties of the Sagittarius dwarf galaxy. Comparing the azimuthal midplane variations in the host galaxy of these simulations before and after the interaction with the Sagittarious-like object gives an idea of the effect of one minor merger whose properties are relatively well measured.

@@

>>>>

The other set of simulations are isolated N-body simulations of interactions between the Milky Way and a Sagittarius-like dwarf galaxy, described briefly in \S \ref{ssec:sag_sim}. These include dark matter and stars and are tailored to existing measurements of the structure of the Milky Way's disk and of the orbit and properties of the Sagittarius dwarf galaxy. Comparing the azimuthal midplane variations in the host galaxy of these simulations before and after the interaction with the Sagittarious-like object gives an idea of the effect of one minor merger whose properties are relatively well measured. Azimuthal variations of the mean vertical height of stars has been explicitly pointed out in a different simulation of a Sagittarius-like encounter by \citet{2013MNRAS.429..159G}.

@@

These values for the midplane variation are consistent with the azimuthal
midplane variations seen by \citet{2013MNRAS.429..159G}. However, they only
saw significant variations in their Heavy but not their Light Sagittarius model (virial masses of $10^{11}\,\Msun$ and
$\sim3\times10^{10}\,\Msun$, respectively). The model we used (L2 from
\citet{2018MNRAS.481..286L}) has a virial mass between these two models of
$6\times10^{10}\,\Msun$.
